A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-08-25 tex/paper.tex
Paper draft ready for SA review

In addition to statistical and systematic error, one might expect that systematic instrumental error might also contribute to the parameter uncertainties. Commonly, one might estimate this error by fitting spectra taken by different instruments or at different times and then averaging the results. Additionally, one may add in an additional uncertainty ``floor'' that maps to the empirical scatter of typical spectroscopic fits. Such procedures generally make the assumption that this additional error contribution is Gaussian and independent in each parameter of interest. Our hierarchical Bayesian model avoids such a heuristic by
parameterizing the quality of fit self-consistently: because the parameter uncertainty is derived through the model itself, it preserves correlations between parameters, like the well known degeneracies between $T_{\rm eff}$, $\log g$, and $\Z$. Arbitrarily inflating the posterior estimates to reflect intuition would artificially destroy any natural degeneracy of parameters. However, for well-calibrated data sets from the same instrument any ill-effects are generally small. To quantify this error contribution for the WASP-14 spectrum in the traditional manner, we independently fit 4 separate \emph{TRES} spectra, and find a minimal scatter of $\sim20$ K and $\lesssim 0.02$ dex in $\Z$. When fitting these 4 spectra simultaneously in a hierarchical manner, we find that \todo{numbers}.

>>>>

In addition to statistical and systematic error, one might expect that
systematic instrumental error might also contribute to the parameter
uncertainties. Commonly, one might estimate this error by fitting spectra taken
by different instruments or at different times and then averaging the results.
Additionally, one may add in an additional uncertainty ``floor'' that maps to
the empirical scatter of typical spectroscopic fits. Such procedures generally
make the assumption that this additional error contribution is Gaussian and
independent in each parameter of interest. Our hierarchical Bayesian model
avoids such a heuristic by parameterizing the quality of fit self-consistently:
because the parameter uncertainty is derived through the model itself, it
preserves correlations between parameters, like the well known degeneracies
between $T_{\rm eff}$, $\log g$, and $\Z$. Arbitrarily inflating the posterior
estimates to reflect intuition would artificially destroy any natural
degeneracy of parameters. However, for well-calibrated data sets from the same
instrument any ill-effects are generally small. To quantify this error
contribution for the WASP-14 spectrum in the traditional manner, we
independently fit 4 separate \emph{TRES} spectra, and find a minimal scatter of
$\sim20$ K and $\lesssim 0.02$ dex in $\Z$. When fitting these 4 spectra
simultaneously in a hierarchical manner, we find that the posteriors shrink by
a similar amount as one would achieve by combining the posterior estimates of
the individual spectra in a weighted average. However, modelling the different
spectra in a simultaneous manner allows us to preserve the intrinsic
correlations between stellar parameters, something that would be destroyed in a
naive weighted average.
